---
title: "Business Intelligence Lab Submission Markdown"
author: "Wisdom"
date: "4/10/2023"
output:
  github_document: 
    toc: yes
    toc_depth: 4
    fig_width: 6
    fig_height: 4
    df_print: default
editor_options:
  chunk_output_type: console
  markdown: 
    wrap: 72
---

# Student Details

|                                 |                                                   |                                                                                                                                                                                                                                                              |
|------------------|------------------|------------------------------------|
|                                 | **Student ID Numbers and Names of Group Members** | *\<list one student name, group, and ID per line; you should be between 2 and 5 members per group\>* \| \| 1. 136714 - A - Meshack Owino \| \| 2. 121717 - A - Celestine Nyaata \| 3. 134455 - A - Arnold Owoko \| \| 4. 135372 - A - Allan Mwandawiro \| \| |
| **GitHub Classroom Group Name** | Wisdom                                            |                                                                                                                                                                                                                                                              |
| **Course Code**                 | BBT4206                                           |                                                                                                                                                                                                                                                              |
| **Course Name**                 | Business Intelligence II                          |                                                                                                                                                                                                                                                              |
| **Program**                     | Bachelor of Business Information Technology       |                                                                                                                                                                                                                                                              |
| **Semester Duration**           | 21^st^ August 2023 to 28^th^ November 2023        |                                                                                                                                                                                                                                                              |

# Setup Chunk

**Note:** the following "*KnitR*" options have been set as the
defaults:\
`knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE, collapse = FALSE, tidy.opts = list(width.cutoff = 80), tidy = TRUE)`.

More KnitR options are documented here
<https://bookdown.org/yihui/rmarkdown-cookbook/chunk-options.html> and
here <https://yihui.org/knitr/options/>.

```{r setup, include=FALSE}
library(formatR)
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE,
                      collapse = FALSE, tidy = TRUE)
```

**Note:** the following "*R Markdown*" options have been set as the
defaults:

> output:\
> \
> github_document:\
> toc: yes\
> toc_depth: 4\
> fig_width: 6\
> fig_height: 4\
> df_print: default\
> \
> editor_options:\
> chunk_output_type: console

# Install and Load required packages

Describe the code chunk here:


Describe the code chunk here:

```{r Your Second Code Chunk}
# Fill this with R related code that will be executed when the R markdown file
# is rendered using knitR
library(readr)
```

#Evaluation of the Students per gender in a plane tabular output

Describe the next code chunk here:

```{r Your Third Code Chunk}
# Fill this with other R related code that will be executed when the R markdown
# file is rendered using knitR
library(readr)
```

#Evaluation of the Students per gender in a visual bar chart

```{r Your Fourth Code Chunk}
# Fill this with other R related code that will be executed when the R markdown
# file is rendered using knitR
library(readr)
```

#Evaluation of the Students per gender in a decorated tabular output

Describe the code chunk here:

```{r Your Fifth Code Chunk}
##The following code evaluates reading of contents before lectures by students per gender in a decorated tabular output

evaluation_per_group_per_gender %>%
  rename(`Class Group` = class_group) %>%
  rename(`Read Before Lecture` = read_content_before_lecture ) %>%
  select(`Class Group`, `Student's Gender`, `Read Before Lecture`) %>%
  mutate(`Read Before Lecture` =
           color_tile("#B9BCC2", "#536CB5")
           (`Read Before Lecture`)) %>%
  kable("html", escape = FALSE, align = "c",
        caption = "Reading Before Lecture Evaluation per Group and per Gender") %>%
  kable_styling(bootstrap_options =
                  c("striped", "condensed", "bordered"),
                full_width = FALSE)
```


#Expand contractions in the English language 

```{r Your Sixth Code Chunk}
##A function to expand contractions in an English-language source

expand_contractions <- function(doc) {
  doc <- gsub("I'm", "I am", doc, ignore.case = TRUE)
  doc <- gsub("you're", "you are", doc, ignore.case = TRUE)
  doc <- gsub("he's", "he is", doc, ignore.case = TRUE)
  doc <- gsub("she's", "she is", doc, ignore.case = TRUE)
  doc <- gsub("it's", "it is", doc, ignore.case = TRUE)
  doc <- gsub("we're", "we are", doc, ignore.case = TRUE)
  doc <- gsub("they're", "they are", doc, ignore.case = TRUE)
  doc <- gsub("I'll", "I will", doc, ignore.case = TRUE)
  doc <- gsub("you'll", "you will", doc, ignore.case = TRUE)
  doc <- gsub("he'll", "he will", doc, ignore.case = TRUE)
  doc <- gsub("she'll", "she will", doc, ignore.case = TRUE)
  doc <- gsub("it'll", "it will", doc, ignore.case = TRUE)
  doc <- gsub("we'll", "we will", doc, ignore.case = TRUE)
  doc <- gsub("they'll", "they will", doc, ignore.case = TRUE)
  doc <- gsub("won't", "will not", doc, ignore.case = TRUE)
  doc <- gsub("can't", "cannot", doc, ignore.case = TRUE)
  doc <- gsub("n't", " not", doc, ignore.case = TRUE)
  return(doc)
}

```

#Student evaluation based on likes and wishes

```{r Your Seventh Code Chunk}

evaluation_likes_and_wishes <- student_performance_dataset %>%
  mutate(`Student's Gender` =
           ifelse(gender == 1, "Male", "Female")) %>%
  rename(`Class Group` = class_group) %>%
  rename(Likes = `D - 1. \nWrite two things you like about the teaching and learning in this unit so far.`) %>% 
  rename(Wishes = `D - 2. Write at least one recommendation to improve the teaching and learning in this unit (for the remaining weeks in the semester)`) %>% 
  select(`Class Group`,
         `Student's Gender`, `Average Course Evaluation Rating`,
         Likes, Wishes) %>%
  filter(!is.na(`Average Course Evaluation Rating`)) %>%
  arrange(`Class Group`)

View(evaluation_likes_and_wishes)

evaluation_likes_and_wishes$Likes <- sapply(evaluation_likes_and_wishes$Likes, expand_contractions) 
evaluation_likes_and_wishes$Wishes <- sapply(evaluation_likes_and_wishes$Wishes, expand_contractions) 

View(evaluation_likes_and_wishes)

```

#Removal of special characters

```{r Your Eighth Code Chunk}

remove_special_characters <- function(doc) {
  gsub("[^a-zA-Z0-9 ]", "", doc, ignore.case = TRUE)
}

View(evaluation_likes_and_wishes)

evaluation_likes_and_wishes$Likes <- sapply(evaluation_likes_and_wishes$Likes, remove_special_characters) 
evaluation_likes_and_wishes$Wishes <- sapply(evaluation_likes_and_wishes$Wishes, remove_special_characters) 


evaluation_likes_and_wishes$Likes <- sapply(evaluation_likes_and_wishes$Likes, tolower) 
evaluation_likes_and_wishes$Wishes <- sapply(evaluation_likes_and_wishes$Wishes, tolower) 

View(evaluation_likes_and_wishes)

```

#Tokenization 

```{r Your Tenth Code Chunk}

evaluation_wishes_filtered <- evaluation_likes_and_wishes %>%
  unnest_tokens(word, Wishes) %>%
  anti_join(stop_words, by = c("word")) %>%
  distinct() %>%
  filter(!word %in% undesirable_words) %>%
  filter(nchar(word) > 3) %>%
  rename(`Wishes (tokenized)` = word) %>%
  select(-Likes)

write.csv(evaluation_wishes_filtered,
          file = "../data/evaluation_wishes_filtered.csv",
          row.names = FALSE)


evaluation_likes_filtered %>%
  select(`Class Group`, `Student's Gender`,
         `Average Course Evaluation Rating`, `Likes (tokenized)`) %>%
  filter(`Student's Gender` == "Female") %>%
  count(`Likes (tokenized)`, sort = TRUE) %>%
  top_n(14) %>%
  mutate(`Likes (tokenized)` = reorder(`Likes (tokenized)`, n)) %>%
  ggplot() +
  geom_col(aes(`Likes (tokenized)`, n), fill = blue_grey_colours_1) +
  blue_grey_theme() +
  xlab("Word in Course Evaluation") +
  ylab("Number of Times Used (Term Frequency)") +
  ggtitle("Most Frequently Used Words in Course Evaluation Likes for Female
          Students") +
  coord_flip()


evaluation_likes_filtered %>%
  select(`Class Group`, `Student's Gender`,
         `Average Course Evaluation Rating`, `Likes (tokenized)`) %>%
  filter(`Student's Gender` == "Male") %>%
  count(`Likes (tokenized)`, sort = TRUE) %>%
  top_n(14) %>%
  mutate(`Likes (tokenized)` = reorder(`Likes (tokenized)`, n)) %>%
  ggplot() +
  geom_col(aes(`Likes (tokenized)`, n), fill = blue_grey_colours_1) +
  blue_grey_theme() +
  xlab("Word in Course Evaluation") +
  ylab("Number of Times Used (Term Frequency)") +
  ggtitle("Most Frequently Used Words in Course Evaluation Likes for Male
          Students") +
  coord_flip()
```

#Evaluation of Likes And Wishes using word cloud

```{r Your Eleventh Code Chunk}
evaluation_likes_filtered_cloud <- evaluation_likes_filtered %>% 
  count(`Likes (tokenized)`, sort = TRUE)

wordcloud2(evaluation_likes_filtered_cloud, size = .7)


evaluation_wishes_filtered_cloud <- evaluation_wishes_filtered %>% 
  count(`Wishes (tokenized)`, sort = TRUE)

wordcloud2(evaluation_wishes_filtered_cloud, size = .6)
```

#Evaluate Importance of a word in a Document using TF-IDF 

```{r Your Twelveth Code Chunk}

popular_tfidf_words_gender_wishes <- evaluation_wishes_filtered %>% 
  unnest_tokens(word, `Wishes (tokenized)`) %>%
  distinct() %>%
  filter(!word %in% undesirable_words) %>%
  filter(nchar(word) > 3) %>%
  rename(`Wishes (tokenized)` = word) %>%
  select(`Class Group`, `Student's Gender`,
         `Average Course Evaluation Rating`, `Wishes (tokenized)`) %>%
  count(`Student's Gender`, `Wishes (tokenized)`, sort = TRUE) %>%
  ungroup() %>%
  bind_tf_idf(`Wishes (tokenized)`, `Student's Gender`, n)

head(popular_tfidf_words_gender_wishes)

top_popular_tfidf_words <- popular_tfidf_words_gender_wishes %>%
  arrange(desc(tf_idf)) %>%
  mutate(`Wishes (tokenized)` =
           factor(`Wishes (tokenized)`,
                  levels = rev(unique(`Wishes (tokenized)`)))) %>%
  group_by(`Student's Gender`) %>%
  slice(seq_len(10)) %>%
  ungroup() %>%
  arrange(`Student's Gender`, tf_idf) %>%
  mutate(row = row_number())

top_popular_tfidf_words %>%
  ggplot(aes(x = row, tf_idf, fill = `Student's Gender`)) +
  geom_col(fill = blue_grey_colours_1) +
  blue_grey_theme() +
  labs(x = "Word in Course Evaluation", y = "TF-IDF Score") +
  ggtitle("Important Words using TF-IDF by Chart Level") +
  ggtitle("Most Important Words by TF-IDF Score in Course Evaluation Wishes per
      Class Group") +
  facet_wrap(~`Student's Gender`, scales = "free") +
  scale_x_continuous(
                     breaks = top_popular_tfidf_words$row,
                     labels = top_popular_tfidf_words$`Wishes (tokenized)`) +
  coord_flip()
```

**etc.** as per the lab submission requirements.
