---
title: "Business Intelligence Lab Submission Markdown"
author: "Wisdom"
date: "4/10/2023"
output:
  github_document: 
    toc: yes
    toc_depth: 4
    fig_width: 6
    fig_height: 4
    df_print: default
editor_options:
  chunk_output_type: console
  markdown: 
    wrap: 72
---

# Student Details

|                                 |                                                   |                                                                                                                                                                                                                                                              |
|------------------|------------------|------------------------------------|
|                                 | **Student ID Numbers and Names of Group Members** | *\<list one student name, group, and ID per line; you should be between 2 and 5 members per group\>* \| \| 1. 136714 - A - Meshack Owino \| \| 2. 121717 - A - Celestine Nyaata \| 3. 134455 - A - Arnold Owoko \| \| 4. 135372 - A - Allan Mwandawiro \| \| |
| **GitHub Classroom Group Name** | Wisdom                                            |                                                                                                                                                                                                                                                              |
| **Course Code**                 | BBT4206                                           |                                                                                                                                                                                                                                                              |
| **Course Name**                 | Business Intelligence II                          |                                                                                                                                                                                                                                                              |
| **Program**                     | Bachelor of Business Information Technology       |                                                                                                                                                                                                                                                              |
| **Semester Duration**           | 21^st^ August 2023 to 28^th^ November 2023        |                                                                                                                                                                                                                                                              |

# Setup Chunk

**Note:** the following "*KnitR*" options have been set as the
defaults:\
`knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE, collapse = FALSE, tidy.opts = list(width.cutoff = 80), tidy = TRUE)`.

More KnitR options are documented here
<https://bookdown.org/yihui/rmarkdown-cookbook/chunk-options.html> and
here <https://yihui.org/knitr/options/>.

```{r setup, include=FALSE}
library(formatR)
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE,
                      collapse = FALSE, tidy = TRUE)
```

**Note:** the following "*R Markdown*" options have been set as the
defaults:

> output:\
> \
> github_document:\
> toc: yes\
> toc_depth: 4\
> fig_width: 6\
> fig_height: 4\
> df_print: default\
> \
> editor_options:\
> chunk_output_type: console

# Install and Load required packages

Describe the code chunk here:


```{r Your First Code Chunk}
.libPaths()
lapply(.libPaths(), list.files)
require("languageserver")
require("dplyr")
require("pandoc")
require("ggplot2")
require("ggrepel")
require("ggraph")
require("tidytext")
require("tidyr")
require("widyr")
require("gridExtra")
require("knitr")
require("kableExtra")
require("formattable")
require("circlize")
require("memery")
require("magick")
require("yarrr")
require("radarchart")
require("igraph")
require("wordcloud2")
require("readr")


blue_grey_colours_11 <- c("#27408E", "#304FAF", "#536CB5", "#6981c7", "#8da0db",
                          "#dde5ec", "#c8c9ca", "#B9BCC2", "#A7AAAF", "#888A8E",
                          "#636569")

blue_grey_colours_6 <- c("#27408E", "#304FAF", "#536CB5",
                         "#B9BCC2", "#A7AAAF", "#888A8E")

blue_grey_colours_4 <- c("#27408E", "#536CB5",
                         "#B9BCC2", "#888A8E")

blue_grey_colours_2 <- c("#27408E",
                         "#888A8E")

blue_grey_colours_1 <- c("#6981c7")


blue_grey_theme <- function() {
  theme(
    axis.ticks = element_line(
                              linewidth = 1, linetype = "dashed",
                              lineend = NULL, color = "#dfdede",
                              arrow = NULL, inherit.blank = FALSE),
    axis.text = element_text(
                             face = "bold", color = "#3f3f41",
                             size = 12, hjust = 0.5),
    axis.title = element_text(face = "bold", color = "#3f3f41",
                              size = 14, hjust = 0.5),
    plot.title = element_text(face = "bold", color = "#3f3f41",
                              size = 16, hjust = 0.5),
    panel.grid = element_line(
                              linewidth = 0.1, linetype = "dashed",
                              lineend = NULL, color = "#dfdede",
                              arrow = NULL, inherit.blank = FALSE),
    panel.background = element_rect(fill = "#f3eeee"),
    legend.title = element_text(face = "plain", color = "#3f3f41",
                                size = 12, hjust = 0),
    legend.position = "right"
  )
}

kable_theme <- function(dat, caption) {
  kable(dat, "html", escape = FALSE, caption = caption) %>%
    kable_styling(bootstrap_options = c("striped", "condensed", "bordered"),
                  full_width = FALSE)
}

```

# \<Provide an Appropriate Title Here\>

Describe the code chunk here:

```{r Your Second Code Chunk}
library(readr)
student_performance_dataset <-
  read_csv("../data/20230412-20230719-BI1-BBIT4-1-StudentPerformanceDataset.CSV",
           col_types =
             cols(
               class_group = col_factor(levels = c("A", "B", "C")),
               gender = col_factor(levels = c("1", "0")),
               YOB = col_date(format = "%Y"),
               regret_choosing_bi = col_factor(levels = c("1", "0")),
               drop_bi_now = col_factor(levels = c("1", "0")),
               motivator = col_factor(levels = c("1", "0")),
               read_content_before_lecture =
                 col_factor(levels = c("1", "2", "3", "4", "5")),
               anticipate_test_questions =
                 col_factor(levels = c("1", "2", "3", "4", "5")),
               answer_rhetorical_questions =
                 col_factor(levels = c("1", "2", "3", "4", "5")),
               find_terms_I_do_not_know =
                 col_factor(levels = c("1", "2", "3", "4", "5")),
               copy_new_terms_in_reading_notebook =
                 col_factor(levels = c("1", "2", "3", "4", "5")),
               take_quizzes_and_use_results =
                 col_factor(levels = c("1", "2", "3", "4", "5")),
               reorganise_course_outline =
                 col_factor(levels = c("1", "2", "3", "4", "5")),
               write_down_important_points =
                 col_factor(levels = c("1", "2", "3", "4", "5")),
               space_out_revision =
                 col_factor(levels = c("1", "2", "3", "4", "5")),
               studying_in_study_group =
                 col_factor(levels = c("1", "2", "3", "4", "5")),
               schedule_appointments =
                 col_factor(levels = c("1", "2", "3", "4", "5")),
               goal_oriented = col_factor(levels = c("1", "0")),
               spaced_repetition =
                 col_factor(levels = c("1", "2", "3", "4")),
               testing_and_active_recall =
                 col_factor(levels = c("1", "2", "3", "4")),
               interleaving = col_factor(levels = c("1", "2", "3", "4")),
               categorizing = col_factor(levels = c("1", "2", "3", "4")),
               retrospective_timetable =
                 col_factor(levels = c("1", "2", "3", "4")),
               cornell_notes = col_factor(levels = c("1", "2", "3", "4")),
               sq3r = col_factor(levels = c("1", "2", "3", "4")),
               commute = col_factor(levels = c("1", "2", "3", "4")),
               study_time = col_factor(levels = c("1", "2", "3", "4")),
               repeats_since_Y1 = col_integer(),
               paid_tuition = col_factor(levels = c("0", "1")),
               free_tuition = col_factor(levels = c("0", "1")),
               extra_curricular = col_factor(levels = c("0", "1")),
               sports_extra_curricular = col_factor(levels = c("0", "1")),
               exercise_per_week = col_factor(levels = c("0", "1", "2", "3")),
               meditate = col_factor(levels = c("0", "1", "2", "3")),
               pray = col_factor(levels = c("0", "1", "2", "3")),
               internet = col_factor(levels = c("0", "1")),
               laptop = col_factor(levels = c("0", "1")),
               family_relationships =
                 col_factor(levels = c("1", "2", "3", "4", "5")),
               friendships = col_factor(levels = c("1", "2", "3", "4", "5")),
               romantic_relationships =
                 col_factor(levels = c("0", "1", "2", "3", "4")),
               spiritual_wellnes =
                 col_factor(levels = c("1", "2", "3", "4", "5")),
               financial_wellness =
                 col_factor(levels = c("1", "2", "3", "4", "5")),
               health = col_factor(levels = c("1", "2", "3", "4", "5")),
               day_out = col_factor(levels = c("0", "1", "2", "3")),
               night_out = col_factor(levels = c("0", "1", "2", "3")),
               alcohol_or_narcotics =
                 col_factor(levels = c("0", "1", "2", "3")),
               mentor = col_factor(levels = c("0", "1")),
               mentor_meetings = col_factor(levels = c("0", "1", "2", "3")),
               `Attendance Waiver Granted: 1 = Yes, 0 = No` =
                 col_factor(levels = c("0", "1")),
               GRADE = col_factor(levels = c("A", "B", "C", "D", "E"))),
           locale = locale())
```

#Evaluation of the Students per gender in a plane tabular output

Describe the next code chunk here:

```{r Your Third Code Chunk}

evaluation_per_group_per_gender <- student_performance_dataset %>% 
  mutate(`Student's Gender` =
           ifelse(gender == 1, "Male", "Female")) %>%
  select(class_group, gender,
         `Student's Gender`,`Average Course Evaluation Rating`, `read_content_before_lecture`) %>%
  filter(!is.na(`Average Course Evaluation Rating`)) %>%
  group_by(class_group,`Student's Gender`,`read_content_before_lecture`) %>%
  summarise(average_evaluation_rating =
              mean(`Average Course Evaluation Rating`)) %>%
  arrange(desc(average_evaluation_rating), .by_group = TRUE)
```

#Evaluation of the Students per gender in a visual bar chart

```{r Your Fourth Code Chunk}

evaluation_per_group_per_gender <- student_performance_dataset %>%
  mutate(`Student's Gender` =
           ifelse(gender == 1, "Male", "Female")) %>%
  select(class_group, gender,
         `Student's Gender`, `Average Course Evaluation Rating`,`read_content_before_lecture`) %>%
  filter(!is.na(`Average Course Evaluation Rating`)) %>%
  group_by(class_group, `Student's Gender`,`read_content_before_lecture`) %>%
  summarise(average_evaluation_rating =
              mean(`Average Course Evaluation Rating`)) %>%
  arrange(desc(average_evaluation_rating), .by_group = TRUE)

View(evaluation_per_group_per_gender)
```

#Evaluation of the Students per gender in a decorated tabular output

Describe the code chunk here:

```{r Your Fifth Code Chunk}
##The following code evaluates reading of contents before lectures by students per gender in a decorated tabular output

evaluation_per_group_per_gender %>%
  rename(`Class Group` = class_group) %>%
  rename(`Read Before Lecture` = read_content_before_lecture ) %>%
  select(`Class Group`, `Student's Gender`, `Read Before Lecture`) %>%
  mutate(`Read Before Lecture` =
           color_tile("#B9BCC2", "#536CB5")
           (`Read Before Lecture`)) %>%
  kable("html", escape = FALSE, align = "c",
        caption = "Reading Before Lecture Evaluation per Group and per Gender") %>%
  kable_styling(bootstrap_options =
                  c("striped", "condensed", "bordered"),
                full_width = FALSE)
```


#Expand contractions in the English language 

```{r Your Sixth Code Chunk}
##A function to expand contractions in an English-language source

expand_contractions <- function(doc) {
  doc <- gsub("I'm", "I am", doc, ignore.case = TRUE)
  doc <- gsub("you're", "you are", doc, ignore.case = TRUE)
  doc <- gsub("he's", "he is", doc, ignore.case = TRUE)
  doc <- gsub("she's", "she is", doc, ignore.case = TRUE)
  doc <- gsub("it's", "it is", doc, ignore.case = TRUE)
  doc <- gsub("we're", "we are", doc, ignore.case = TRUE)
  doc <- gsub("they're", "they are", doc, ignore.case = TRUE)
  doc <- gsub("I'll", "I will", doc, ignore.case = TRUE)
  doc <- gsub("you'll", "you will", doc, ignore.case = TRUE)
  doc <- gsub("he'll", "he will", doc, ignore.case = TRUE)
  doc <- gsub("she'll", "she will", doc, ignore.case = TRUE)
  doc <- gsub("it'll", "it will", doc, ignore.case = TRUE)
  doc <- gsub("we'll", "we will", doc, ignore.case = TRUE)
  doc <- gsub("they'll", "they will", doc, ignore.case = TRUE)
  doc <- gsub("won't", "will not", doc, ignore.case = TRUE)
  doc <- gsub("can't", "cannot", doc, ignore.case = TRUE)
  doc <- gsub("n't", " not", doc, ignore.case = TRUE)
  return(doc)
}

```

#Student evaluation based on likes and wishes

```{r Your Seventh Code Chunk}

evaluation_likes_and_wishes <- student_performance_dataset %>%
  mutate(`Student's Gender` =
           ifelse(gender == 1, "Male", "Female")) %>%
  rename(`Class Group` = class_group) %>%
  rename(Likes = `D - 1. \nWrite two things you like about the teaching and learning in this unit so far.`) %>% 
  rename(Wishes = `D - 2. Write at least one recommendation to improve the teaching and learning in this unit (for the remaining weeks in the semester)`) %>% 
  select(`Class Group`,
         `Student's Gender`, `Average Course Evaluation Rating`,
         Likes, Wishes) %>%
  filter(!is.na(`Average Course Evaluation Rating`)) %>%
  arrange(`Class Group`)

View(evaluation_likes_and_wishes)

evaluation_likes_and_wishes$Likes <- sapply(evaluation_likes_and_wishes$Likes, expand_contractions) 
evaluation_likes_and_wishes$Wishes <- sapply(evaluation_likes_and_wishes$Wishes, expand_contractions) 

View(evaluation_likes_and_wishes)

```

#Removal of special characters

```{r Your Eighth Code Chunk}

remove_special_characters <- function(doc) {
  gsub("[^a-zA-Z0-9 ]", "", doc, ignore.case = TRUE)
}

View(evaluation_likes_and_wishes)

evaluation_likes_and_wishes$Likes <- sapply(evaluation_likes_and_wishes$Likes, remove_special_characters) 
evaluation_likes_and_wishes$Wishes <- sapply(evaluation_likes_and_wishes$Wishes, remove_special_characters) 


evaluation_likes_and_wishes$Likes <- sapply(evaluation_likes_and_wishes$Likes, tolower) 
evaluation_likes_and_wishes$Wishes <- sapply(evaluation_likes_and_wishes$Wishes, tolower) 

View(evaluation_likes_and_wishes)

```

#Tokenization 

```{r Your Tenth Code Chunk}

evaluation_wishes_filtered <- evaluation_likes_and_wishes %>%
  unnest_tokens(word, Wishes) %>%
  anti_join(stop_words, by = c("word")) %>%
  distinct() %>%
  filter(!word %in% undesirable_words) %>%
  filter(nchar(word) > 3) %>%
  rename(`Wishes (tokenized)` = word) %>%
  select(-Likes)

write.csv(evaluation_wishes_filtered,
          file = "../data/evaluation_wishes_filtered.csv",
          row.names = FALSE)


evaluation_likes_filtered %>%
  select(`Class Group`, `Student's Gender`,
         `Average Course Evaluation Rating`, `Likes (tokenized)`) %>%
  filter(`Student's Gender` == "Female") %>%
  count(`Likes (tokenized)`, sort = TRUE) %>%
  top_n(14) %>%
  mutate(`Likes (tokenized)` = reorder(`Likes (tokenized)`, n)) %>%
  ggplot() +
  geom_col(aes(`Likes (tokenized)`, n), fill = blue_grey_colours_1) +
  blue_grey_theme() +
  xlab("Word in Course Evaluation") +
  ylab("Number of Times Used (Term Frequency)") +
  ggtitle("Most Frequently Used Words in Course Evaluation Likes for Female
          Students") +
  coord_flip()


evaluation_likes_filtered %>%
  select(`Class Group`, `Student's Gender`,
         `Average Course Evaluation Rating`, `Likes (tokenized)`) %>%
  filter(`Student's Gender` == "Male") %>%
  count(`Likes (tokenized)`, sort = TRUE) %>%
  top_n(14) %>%
  mutate(`Likes (tokenized)` = reorder(`Likes (tokenized)`, n)) %>%
  ggplot() +
  geom_col(aes(`Likes (tokenized)`, n), fill = blue_grey_colours_1) +
  blue_grey_theme() +
  xlab("Word in Course Evaluation") +
  ylab("Number of Times Used (Term Frequency)") +
  ggtitle("Most Frequently Used Words in Course Evaluation Likes for Male
          Students") +
  coord_flip()
```

#Evaluation of Likes And Wishes using word cloud

```{r Your Eleventh Code Chunk}
evaluation_likes_filtered_cloud <- evaluation_likes_filtered %>% 
  count(`Likes (tokenized)`, sort = TRUE)

wordcloud2(evaluation_likes_filtered_cloud, size = .7)


evaluation_wishes_filtered_cloud <- evaluation_wishes_filtered %>% 
  count(`Wishes (tokenized)`, sort = TRUE)

wordcloud2(evaluation_wishes_filtered_cloud, size = .6)
```

#Evaluate Importance of a word in a Document using TF-IDF 

```{r Your Twelveth Code Chunk}

popular_tfidf_words_gender_wishes <- evaluation_wishes_filtered %>% 
  unnest_tokens(word, `Wishes (tokenized)`) %>%
  distinct() %>%
  filter(!word %in% undesirable_words) %>%
  filter(nchar(word) > 3) %>%
  rename(`Wishes (tokenized)` = word) %>%
  select(`Class Group`, `Student's Gender`,
         `Average Course Evaluation Rating`, `Wishes (tokenized)`) %>%
  count(`Student's Gender`, `Wishes (tokenized)`, sort = TRUE) %>%
  ungroup() %>%
  bind_tf_idf(`Wishes (tokenized)`, `Student's Gender`, n)

head(popular_tfidf_words_gender_wishes)

top_popular_tfidf_words <- popular_tfidf_words_gender_wishes %>%
  arrange(desc(tf_idf)) %>%
  mutate(`Wishes (tokenized)` =
           factor(`Wishes (tokenized)`,
                  levels = rev(unique(`Wishes (tokenized)`)))) %>%
  group_by(`Student's Gender`) %>%
  slice(seq_len(10)) %>%
  ungroup() %>%
  arrange(`Student's Gender`, tf_idf) %>%
  mutate(row = row_number())

top_popular_tfidf_words %>%
  ggplot(aes(x = row, tf_idf, fill = `Student's Gender`)) +
  geom_col(fill = blue_grey_colours_1) +
  blue_grey_theme() +
  labs(x = "Word in Course Evaluation", y = "TF-IDF Score") +
  ggtitle("Important Words using TF-IDF by Chart Level") +
  ggtitle("Most Important Words by TF-IDF Score in Course Evaluation Wishes per
      Class Group") +
  facet_wrap(~`Student's Gender`, scales = "free") +
  scale_x_continuous(
                     breaks = top_popular_tfidf_words$row,
                     labels = top_popular_tfidf_words$`Wishes (tokenized)`) +
  coord_flip()
```

# \<You can Provide Another Appropriate Title Here\>

```{r Your Sixth Code Chunk}

evaluation_per_group_per_gender %>%
  ggplot() +
  geom_bar(aes(x = class_group, y = read_content_before_lecture,
               fill = `Student's Gender`),
           stat = "identity", position = "dodge") +
  expand_limits(y = 0) +
  blue_grey_theme() +
  scale_fill_manual(values = blue_grey_colours_2) +
  ggtitle("Reading Before Lecture Evaluation per Group and per Gender") +
  labs(x = "Class Group", y = "Average Rating")

```

# \<You can Provide Another Appropriate Title Here\>

```{r Your Seventh Code Chunk}

expand_contractions <- function(doc) {
  doc <- gsub("I'm", "I am", doc, ignore.case = TRUE)
  doc <- gsub("you're", "you are", doc, ignore.case = TRUE)
  doc <- gsub("he's", "he is", doc, ignore.case = TRUE)
  doc <- gsub("she's", "she is", doc, ignore.case = TRUE)
  doc <- gsub("it's", "it is", doc, ignore.case = TRUE)
  doc <- gsub("we're", "we are", doc, ignore.case = TRUE)
  doc <- gsub("they're", "they are", doc, ignore.case = TRUE)
  doc <- gsub("I'll", "I will", doc, ignore.case = TRUE)
  doc <- gsub("you'll", "you will", doc, ignore.case = TRUE)
  doc <- gsub("he'll", "he will", doc, ignore.case = TRUE)
  doc <- gsub("she'll", "she will", doc, ignore.case = TRUE)
  doc <- gsub("it'll", "it will", doc, ignore.case = TRUE)
  doc <- gsub("we'll", "we will", doc, ignore.case = TRUE)
  doc <- gsub("they'll", "they will", doc, ignore.case = TRUE)
  doc <- gsub("won't", "will not", doc, ignore.case = TRUE)
  doc <- gsub("can't", "cannot", doc, ignore.case = TRUE)
  doc <- gsub("n't", " not", doc, ignore.case = TRUE)
  return(doc)
}

```

# \<You can Provide Another Appropriate Title Here\>

```{r Your Eighth Code Chunk}

evaluation_likes_and_wishes <- student_performance_dataset %>%
  mutate(`Student's Gender` =
           ifelse(gender == 1, "Male", "Female")) %>%
  rename(`Class Group` = class_group) %>%
  rename(Likes = `D - 1. \nWrite two things you like about the teaching and learning in this unit so far.`) %>% 
  rename(Wishes = `D - 2. Write at least one recommendation to improve the teaching and learning in this unit (for the remaining weeks in the semester)`) %>% 
  select(`Class Group`,
         `Student's Gender`, `Average Course Evaluation Rating`,
         Likes, Wishes) %>%
  filter(!is.na(`Average Course Evaluation Rating`)) %>%
  arrange(`Class Group`)

View(evaluation_likes_and_wishes)

evaluation_likes_and_wishes$Likes <- sapply(evaluation_likes_and_wishes$Likes, expand_contractions) 
evaluation_likes_and_wishes$Wishes <- sapply(evaluation_likes_and_wishes$Wishes, expand_contractions) 

View(evaluation_likes_and_wishes)

```

# \<You can Provide Another Appropriate Title Here\>

```{r Your Nineth Code Chunk}

remove_special_characters <- function(doc) {
  gsub("[^a-zA-Z0-9 ]", "", doc, ignore.case = TRUE)
}

View(evaluation_likes_and_wishes)

evaluation_likes_and_wishes$Likes <- sapply(evaluation_likes_and_wishes$Likes, remove_special_characters) 
evaluation_likes_and_wishes$Wishes <- sapply(evaluation_likes_and_wishes$Wishes, remove_special_characters) 


evaluation_likes_and_wishes$Likes <- sapply(evaluation_likes_and_wishes$Likes, tolower) 
evaluation_likes_and_wishes$Wishes <- sapply(evaluation_likes_and_wishes$Wishes, tolower) 

View(evaluation_likes_and_wishes)

```



**etc.** as per the lab submission requirements.
